\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-19 doc/USER_MANUAL/manual_SPECFEM3D.tex
changed "manual's cover graphic" to "cover graphic of the manual"

The manual's cover graphic was created
by Santiago Lombeyda from Caltech's Center for Advanced Computing Research (CACR) \url{http://www.cacr.caltech.edu}.
Sue Kientz assembled the manual.\\

>>>>

The cover graphic of the manual was created
by Santiago Lombeyda from Caltech's Center for Advanced Computing Research (CACR) \url{http://www.cacr.caltech.edu}.
Sue Kientz assembled the manual.\\
